### 2017-12-31 icde/revision/sec-exp.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t!]
%\vspace{-2ex}
\label{tab-result}
\begin{center}
\caption{\small Memory costs on \aminer and \magdata}
%\begin{small}
\vspace{-.5ex}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
{\bf Datasets}   &  Data     &  \pagerank     & \futurerank  &  \hhgrank  &   \ensemblerank    \\
\hline \hline
%\aan  & 6.80MB   & 5.03MB   & 5.86MB   & 11.06MB     & 13.09MB      \\  %\hline
%\aminer  & 288.87MB   & 263.81MB   & 404.46MB   & 1.34GB     & 1.28GB      \\ %\hline
%\magdata  & 10.46GB   & 8.67GB   & 14.32GB   & 61.37GB     & 48.13GB      \\ \hline
%\aan  & 6.8MB   & 5.03MB   & 5.86MB   & 11.06MB     & 13.09MB      \\  %\hline
\aminer  & 289MB   & 264MB   & 404MB   & 1.34GB     & 1.28GB      \\ %\hline
\magdata  & 10.5GB   & 8.7GB   & 14.3GB   & 61.4GB     & 48.1GB      \\ \hline
\end{tabular}
%\vspace{-.5ex}
%\end{small}
\end{center}
\vspace{-6ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

\stitle{Exp-4: Memory cost}.
%
In the fourth set of tests, we evaluated the memory cost of our algorithm on the large \aminer and \magdata. For a fair comparison, we used all data on \aminer and data before 2014 on \magdata such that \hhgrank can finish the test. The results are reported in Table~IV, where the Data column records the size of the academic graph data, \ie the citation graph, author-article relationships, article-venue relationships and time information of articles.

On both datasets, algorithm \pagerank uses the least memory, followed by algorithms \futurerank, \ensemblerank and \hhgrank, respectively. 
%
The memory used by \pagerank is even less than the size of data as it is based on the citation graph only.
%
Our \ensemblerank model costs more memory than \futurerank since it also combines article-venue relationships ignored by \futurerank and it assembles multiple rankings based on prestige and popularity. However, our \ensemblerank model is still more memory-efficient than \hhgrank. 
%
To conclude, the \ensemblerank model uses reasonable amount of  memory to achieve the better effectiveness.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t!]
%\vspace{-2ex}
\label{tab-mem-result}
\begin{center}
\caption{\small Memory costs on \aminer and \magdata}
%\begin{small}
\vspace{-.5ex}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
{\bf Datasets}   &  Data     &  \pagerank     & \futurerank  &  \hhgrank  &   \ensemblerank    \\
\hline \hline
%\aan  & 6.80MB   & 5.03MB   & 5.86MB   & 11.06MB     & 13.09MB      \\  %\hline
%\aminer  & 288.87MB   & 263.81MB   & 404.46MB   & 1.34GB     & 1.28GB      \\ %\hline
%\magdata  & 10.46GB   & 8.67GB   & 14.32GB   & 61.37GB     & 48.13GB      \\ \hline
%\aan  & 6.8MB   & 5.03MB   & 5.86MB   & 11.06MB     & 13.09MB      \\  %\hline
\aminer  & 289MB   & 264MB   & 404MB   & 1.34GB     & 1.28GB      \\ %\hline
\magdata  & 10.5GB   & 8.7GB   & 14.3GB   & 61.4GB     & 48.1GB      \\ \hline
\end{tabular}
%\vspace{-.5ex}
%\end{small}
\end{center}
\vspace{-6ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

\stitle{Exp-4: Memory cost}.
%
In the fourth set of tests, we evaluated the memory cost of our algorithm on the large \aminer and \magdata. For a fair comparison, we used all data on \aminer and data before 2014 on \magdata such that \hhgrank could finish the test. The results are reported in Table~IV, where column `Data' records the size of the academic graph data, \ie the citation graph, author-article relationships, article-venue relationships and time information of articles.

Algorithm \pagerank uses the least memory, followed by algorithms \futurerank, \ensemblerank and \hhgrank, respectively.
%
The memory used by \pagerank is even less than the data size as it uses the citation graph only.
%
Our \ensemblerank model costs more memory than \futurerank, but less than \hhgrank.
This is because \ensemblerank further combines article-venue relationships ignored by \futurerank, and assembles multiple rankings based on prestige and popularity,
a price paid to achieve better effectiveness.
